DeepSphere: a graph-based spherical CNN

### 2019-09-25 main.tex
cleaned abstract
Updates from Overleaf

% 3.0) explain how we obtained the figures
We calculated numerically the equivariance error \eqref{eq:mean equivariance error} for different parameter sets of DeepSphere and for the graph of Khasanova and Frossard. We approximated equation \eqref{eq:mean equivariance error} by calculating the empirical average of the equivariance errors of $N$ random monochromatic signals on $M$ random rotations for each signal. Results are in figure \ref{fig:equivariance_error}.
The frequencies of the monochromatic signals, on the x axis in figure \ref{fig:equivariance_error}, were chosen in the range $(0,\  3N_{side}-1)$ to allow for an almost perfect synthesis of the sampled signals, and thus an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ in equation \eqref{eq:mean equivariance error} \citep{gorski1999healpixprimer}. In this way all the error measured is due to imperfections in the empirical approximation of the Laplace-Beltrami operator.

@@

\begin{figure}
	\begin{minipage}{0.65\linewidth}
		\centering
		\includegraphics[width=\linewidth]{all_in_one.pdf}
		\caption{Equivariance error.}
		\label{fig:equivariance_error}
	\end{minipage}
	\hfill
	\begin{minipage}{0.35\linewidth}
		\centering
		\includegraphics[width=\linewidth]{kernel_widths}
		\caption{Optimal kernel widths.}
		\label{fig:kernel_widths}
		\vspace{1em}
		\includegraphics[height=4.5em]{lamp_000018}
		\hfill
		\includegraphics[height=4.5em]{lamp_000018_sphere_nobar}
		\caption{3D object represented as a spherical depth map.}
		\label{fig:depthmap}
		\vspace{1em}
		\includegraphics[width=\linewidth]{spectrum}
		\caption{Power spectral densities.}
		\label{fig:spectrum}
	\end{minipage}
\end{figure}

>>>>

% 3.0) explain how we obtained the figures
We calculated numerically the equivariance error \eqref{eq:mean equivariance error} for monochromatic signals, for different parameter sets of DeepSphere and for the graph of Khasanova and Frossard. We approximated equation \eqref{eq:mean equivariance error} by calculating the empirical average of the equivariance errors of $N$ random monochromatic signals on $M$ random rotations for each signal. Results are in figure \ref{fig:equivariance_error}.
The frequencies of the monochromatic signals, on the x axis in figure \ref{fig:equivariance_error}, were chosen in the range $(0,\  3N_{side}-1)$ to allow for an almost perfect synthesis of the sampled signals, and thus an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ in equation \eqref{eq:mean equivariance error} \citep{gorski1999healpixprimer}. In this way all the error measured is due to imperfections in the empirical approximation of the Laplace-Beltrami operator.

@@

\begin{figure}
	\begin{minipage}{0.65\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{all_in_one.pdf}
		\caption{Equivariance error. The number of pixels is $4*s^2$ equiangular =

Npix for healpix = 12*nside**2}
		\label{fig:equivariance_error}
	\end{minipage}
	\hfill
	\begin{minipage}{0.35\linewidth}
		\centering
		\includegraphics[width=\linewidth]{kernel_widths}
		\caption{Optimal kernel widths.}
		\label{fig:kernel_widths}
		\vspace{1em}
		\includegraphics[height=4.5em]{lamp_000018}
		\hfill
		\includegraphics[height=4.5em]{lamp_000018_sphere_nobar}
		\caption{3D object represented as a spherical depth map.}
		\label{fig:depthmap}
		\vspace{1em}
		\includegraphics[width=\linewidth]{spectrum}
		\caption{Power spectral densities.}
		\label{fig:spectrum}
	\end{minipage}
\end{figure}
